\EVOSUITE at the SBST 2019 Tool Competition

### 2019-03-23 papers/sbst19/paper_sbst19.tex
Add text on infrastructure problem

For the AUTHZFORCE benchmarks, although \EVOSUITE managed to generate some test
suites, most executions ended with a failure, unfortunately, we have not been
able to reproduce this behaviour locally, hence we cannot conjecture the reason
of such failures. \TODO{exact the same happened for SPOON-253 (120s and 240s).
Some sort of java.lang.SecurityException: Security manager blocks ("java.lang.RuntimePermission" "setSecurityManager").}

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to
\EVOSUITE.  This project has been funded by the EPSRC project
``GREATEST'' (EP/N023978/1), and by the National Research Fund,
Luxembourg (FNR/P10/03). \TODO{update}

>>>>

For the AUTHZFORCE benchmarks, although \EVOSUITE managed to generate
some test suites, most executions for data collection ended with a
failure. Specifically, for these classes an exception was raised for
test execution for \emph{all} tools in the competition. However,
while this exception was not problematic for other tools, it caused
an inconsistent state of the JVM which led to the \texttt{@Before}
setup methods of \EVOSUITE to fail (the \texttt{@Before} method was
not able to configure \EVOSUITE's custom security manager because it
was never correctly removed). As a consequence, all test executions
failed. We were not able to reproduce the error in the competition
infrastructure, and thus cannot conjecture about the causes. The same
problem also occurred for SPOON-253. While in principle it would be
possible to extend \EVOSUITE to try to ignore such errors and keep on
executing tests, as explained it is \EVOSUITE's philosophy that the
user should be made aware of configuration errors, and hence such an
extension would only serve to tune \EVOSUITE for the competition.

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to
\EVOSUITE.  This project has been funded by the EPSRC project
``GREATEST'' (EP/N023978/2), and by the National Research Fund,
Luxembourg (FNR/P10/03). \TODO{update}
